### 2023-03-27 Manuscript/Draft1.Rmd
small updates

Fish stocks in this highly productive and economically important region are managed by the National Oceanic and Atmospheric Administration’s (NOAA) Northeast Fisheries Science Center (NEFSC) in Woods Hole, Massachusetts. Federal scientists assess the health and abundance of each commercial fish stock using fishery-independent bottom trawl survey data that has been collected by NOAA throughout the region since 1963 [@azarovitz1981brief; @politis2014northeast]. The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits. The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and  projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling Georges Bank during approximately the same 3-4 week time period in each season.

<!-- Paragraph above: Stocks in this region are not managed by NEFSC, they are assessed by us. The management is done by the Councils and GARFO. NEFSC actually only assesses the federally managed stocks (not the state managed stocks like tautog). We also assess some of the invertebrate stocks, such as squid, scallops, ocean quahogs, etc., in addition to fish stocks. Perhaps easier to focus on the bottom trawl itself and replace the first two sentences with something like The NEFSC has conducted a bottom trawl survey since 1963 to support assessment and management of the fish and invertebrate populations in the region (azaorivitz and politis refs).  -->

>>>>

The NEFSC has conducted a bottom trawl survey since 1963 to support assessment and management of the fish and invertebrate populations in the region [@azarovitz1981brief; @politis2014northeast]. The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits. The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and  projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling Georges Bank during approximately the same 3-4 week time period in each season.

### 2023-03-27 Manuscript/Draft1.tex
small updates

Fish stocks in this highly productive and economically important region are managed by the National Oceanic and Atmospheric Administration's (NOAA) Northeast Fisheries Science Center (NEFSC) in Woods Hole, Massachusetts. Federal scientists assess the health and abundance of each commercial fish stock using fishery-independent bottom trawl survey data that has been collected by NOAA throughout the region since 1963 (Azarovitz 1981; Politis et al. 2014). The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits. The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling Georges Bank during approximately the same 3-4 week time period in each season.

>>>>

The NEFSC has conducted a bottom trawl survey since 1963 to support assessment and management of the fish and invertebrate populations in the region (Azarovitz 1981; Politis et al. 2014). The survey uses a stratified random design where bottom trawl sampling takes place in predefined strata along the eastern continental shelf. The survey has created a rich time series data set with many uses including species-specific habitat identification, analysis of how environmental conditions influence species abundance, and estimating yearly species abundance trends to help inform stock assessments and ultimately quota limits. The survey takes place twice each year- once in the spring and again in the fall. Since most spatial analyses and projections of future distributions typically assume a constant survey catchability and/or availability over time, NOAA's survey design includes sampling Georges Bank during approximately the same 3-4 week time period in each season.
